% Company-specific configuration for NASA
% Overrides base_config.tex defaults using \renewcommand
% Only define fields that differ from base defaults

%-----------COMPANY DETAILS------------
\renewcommand{\companyrecipient}{NASA Recruitment Team}
\renewcommand{\companyname}{NASA}
\renewcommand{\companyaddress}{300 E Street SW}
\renewcommand{\companycity}{Washington, DC 20546}

%-----------COVER LETTER SETTINGS------------
\renewcommand{\letterdatelanguage}{english}
\renewcommand{\letterdate}{auto}
\renewcommand{\letterclosing}{Sincerely}
\renewcommand{\letteropening}{Dear Hiring Manager,}
\renewcommand{\lettertitle}{Job Application for Distinguished Engineer}
\renewcommand{\letterattachment}{Attached: Curriculum Vitae}

% Letter Content (company example)
\providecommand{\letteraboutme}{}%
\renewcommand{\letteraboutme}{%
  I’m applying for the Distinguished Engineer role because I enjoy building and operating systems where correctness, traceability, and reliability matter. I’ve led large-scale platform work across distributed services and data pipelines, and I’m comfortable translating ambiguous mission goals into concrete technical plans, measurable risk reduction, and steady delivery.
}

% Why [Company Name]? section - explain your interest in the company
\providecommand{\letterwhycompany}{}%
\renewcommand{\letterwhycompany}{%
  NASA’s missions demand engineering discipline: clear interfaces, robust verification, and thoughtful operational readiness. I’m especially motivated by work that spans flight and ground software, where telemetry, automation, and incident response directly improve mission safety and outcomes.
}

% Why Me? section - highlight your qualifications and fit for the role
\providecommand{\letterwhyme}{}%
\renewcommand{\letterwhyme}{%
  I bring a systems approach and a strong bias for operational excellence: designing for observability, validating assumptions with data, and treating reliability as a product feature. I’m effective in cross-functional environments—aligning stakeholders, setting engineering standards, and mentoring teams to deliver high-assurance software at scale.
}

% Impact highlights (for bullet-style cover letter variant)
\renewcommand{\letterhighlights}{%
  \item Reduced mission-critical processing time by 42\% by redesigning scheduling, telemetry ingestion, and backpressure handling.
  \item Led cross-team incident response and blameless postmortems; cut repeat incidents by 30\% through systematic remediation.
  \item Built automated validation for configuration and deployment artifacts, catching regressions pre-release and improving launch confidence.
}

%-----------CV CUSTOMIZATIONS------------
\renewcommand{\cvtitle}{Space Systems Engineer | Flight Software Specialist}

% Technologies section - Skills format (Technical and Soft Skills)
\renewcommand{\cvtechnologies}{%
  \section{Skills}
  \resumeSubHeadingListStart
    \item{\textbf{Technical Skills}{:} Space Systems, Satellite Operations, Mission Control, Ground Systems, AWS, Azure, Docker, Kubernetes, Python, C++, Rust, Go, MATLAB, Real-time Systems, Embedded Systems, Flight Software} \vspace{-8pt}
    \item{\textbf{Soft Skills}{:} Problem-solving, Critical thinking, Strategic planning, Continuous learning, Communication, Attention to detail, Safety-first mindset}
  \resumeSubHeadingListEnd
}

% Certificates (reduced to 5 to fit on one page with both degrees)
% Example: some with links, some without
% Replace YOUR_BADGE_ID with your actual Credly badge ID from your Credly profile
\renewcommand{\cvcertificates}{%
  \href{https://www.credly.com/badges/YOUR_AWS_SA_PRO_BADGE_ID}{\textbf{AWS Certified Solutions Architect – Professional}} & \textcolor{gray}{\textit{May 2022 - May 2025}} \\
  \href{https://www.credly.com/badges/YOUR_AWS_DEVOPS_PRO_BADGE_ID}{\textbf{AWS Certified DevOps Engineer – Professional}} & \textcolor{gray}{\textit{May 2019 - May 2022}} \\
  \textbf{CKA: Certified Kubernetes Administrator} & \textcolor{gray}{\textit{Aug 2024 - Aug 2026}} \\
  \href{https://www.credly.com/badges/YOUR_MS_DEVOPS_BADGE_ID}{\textbf{Microsoft Certified: DevOps Engineer Expert}} & \textcolor{gray}{\textit{Jan 2021 - Jan 2026}} \\
  \textbf{Microsoft Certified: Azure Administrator Associate} & \textcolor{gray}{\textit{Jan 2021 - Jan 2026}}
}

% Open Source Contributions (none - explicitly set to empty)
\renewcommand{\cvopensource}{}

% Volunteer Work (NASA example: space education outreach)
\renewcommand{\cvvolunteer}{%
  \resumeSubheading
    {Space Education Foundation}{\textcolor{gray}{Remote}}
    {Volunteer Mentor}{\textcolor{gray}{2020 -- Present}}
  \resumeItemListStart
    \resumeItemSimple{}
      {Mentoring students in space systems engineering. Conducting workshops on satellite operations.}
  \resumeItemListEnd
}

% Languages (none - leave empty to save space)
\renewcommand{\cvlanguages}{}

% Awards (none - leave empty)
\renewcommand{\cvawards}{}

